### 2023-03-30 resilience-safe-up.tex
\Bad = up \Bad \ßetminus \Safe replaced with an U, small parazgraph about motivation need to be expanded upon slightly

\subsection{Case: $\Safe=\uparrow \Safe$ and $\Bad=\uparrow \Bad \setminus \Safe$.}

@@

@@

\begin{theorem}\label{up-up}
The resilience problem is decidable for effective WSTS with effective pred-basis, $\Safe=\uparrow \Safe$
and $\Bad=\uparrow \Bad \setminus \Safe$.

@@

\begin{proof}
Since $\Safe=\uparrow \Safe$ is upward closed, there exists a finite basis $B_{ \Safe}$ such that $\uparrow \Safe = \uparrow B_{\Safe}$. 
Moreover since $\mathscr{S}=(S,\rightarrow,\leq)$ is a WTSTS,  $\pred^*(\Safe)=\uparrow \pred^*(\Safe)$ and $\pred^*(\Safe)$ admits a finite basis $B_{\pred^*(\Safe)}$. Since $\mathscr{S}=(S,\rightarrow,\leq)$ is a WSTS  with effective pred-basis, we may compute a finite basis of $\pred^*(\Safe)$ with the backward coverability algorithm. 
Since $\uparrow \Bad$  is upward closed, there exists a finite basis $B_{\uparrow \Bad}$ such that $\uparrow \Bad = \uparrow B_{\uparrow \Bad}$. % Moreover $ \uparrow B_{\Bad} \subseteq \uparrow B_{\pred^*(\Safe)}$ iff for every $b \in B_{\Bad}$, there is a $s \in B_{\pred^*(\Safe)}$ such that $s \leq b$.
Since $\Bad = \uparrow \Bad \setminus \Safe$, $\Bad \subseteq \uparrow B_{\pred^*(\Safe)}$ iff for every $b \in B_{\Bad}$, there is either $s \in B_{\pred^*(\Safe)}$ such that $s \leq b$, either $t \in B_{\Safe}$ such that $t\leq b$,
% si on est dans up Bad, il faut que ou bien on soit dans pred(Safe) ou bien on soit dans Safe
hence the resilience problem is decidable.
\end{proof}

@@

\begin{corollary}\label{B-up-up}
The bounded resilience problem is decidable for WSTS with effective pred-basis,
strong compatibility
 $\Safe=\uparrow \Safe$
and $\Bad=\uparrow \Bad$.
\end{corollary}

\begin{theorem}\label{k-up-up}
The % three %uniform 
$k$-resilience problem is decidable for WSTS with effective pred-basis, strong %upward-
compatibility, $\Safe=\uparrow \Safe$
and $\Bad=\uparrow \Bad \setminus \Safe$.
%	and \Bad is upward closed or downward closed.
\end{theorem}

\begin{proof}
Since $\Safe=\uparrow \Safe$ is upward closed, there exists a finite basis $B_{ \Safe}$ such that $\uparrow \Safe = \uparrow B_{\Safe}$. 
Moreover since $\mathscr{S}=(S,\rightarrow,\leq)$ is a WTSTS with strong upward compatibility,  $\pred^n(\Safe)=\uparrow \pred^n(\Safe)$ for all $n\in \N$ and $\pred^{\leq k}(\Safe)$ admits a finite basis $B_{\pred^{\leq k}(\Safe)}$. % Since $\mathscr{S}=(S,\rightarrow,\leq)$ is a WSTS  with effective pred-basis, we may compute a finite basis of $\pred^{\leq k}(\Safe)$ with the backward coverability algorithm. 
Since $\uparrow \Bad$  is upward closed, there exists a finite basis $B_{\uparrow \Bad}$ such that $\uparrow \Bad = \uparrow B_{\uparrow \Bad}$. % Moreover $ \uparrow B_{\Bad} \subseteq \uparrow B_{\pred^{\leq k}(\Safe)}$ iff for every $b \in B_{\Bad}$, there is a $s \in B_{\pred^*(\Safe)}$ such that $s \leq b$.
Since $\Bad = \uparrow \Bad \setminus \Safe$, $\Bad \subseteq \uparrow B_{\pred^{\leq k}(\Safe)}$ iff for every $b \in B_{\Bad}$, there is either $s \in B_{\pred^{\leq k}(\Safe)}$ such that $s \leq b$, either $t \in B_{\Safe}$ such that $t\leq b$,
% si on est dans up Bad, il faut que ou bien on soit dans pred(Safe) ou bien on soit dans Safe
hence the resilience problem is decidable.
\end{proof}

>>>>

\subsection{Case: $\Safe=\uparrow \Safe$ and $\Bad = ... $.}

@@

Since we impose $\Bad \cap \Safe = \emptyset$, we cannot have as an hypothesis
both $\Safe = \uparrow \Safe$ and $\Bad = \uparrow \Bad$. To approximate a case
of double upward closure, we consider a case where $\Bad$ is as upward-closed
as it can be without intersecting with $\Safe$,
i.e. 
such that there exists an upward closed set $U$
such that $\Bad = U \setminus \Safe$.
Morally speaking ... [].

@@

\begin{theorem}\label{up-up}
The resilience problem is decidable for effective WSTS with effective pred-basis, $\Safe=\uparrow \Safe$
and $\Bad= U \setminus \Safe$.

@@

\begin{proof}
Since $\Safe=\uparrow \Safe$ is upward closed, there exists a finite basis $B_{ \Safe}$ such that $\uparrow \Safe = \uparrow B_{\Safe}$. 
Moreover since $\mathscr{S}=(S,\rightarrow,\leq)$ is a WTSTS,  $\pred^*(\Safe)=\uparrow \pred^*(\Safe)$ and $\pred^*(\Safe)$ admits a finite basis $B_{\pred^*(\Safe)}$. Since $\mathscr{S}=(S,\rightarrow,\leq)$ is a WSTS  with effective pred-basis, we may compute a finite basis of $\pred^*(\Safe)$ with the backward coverability algorithm. 
Since $U$  is upward closed, there exists a finite basis $B_{U}$ such that $U = \uparrow B_{U}$. % Moreover $ \uparrow B_{\Bad} \subseteq \uparrow B_{\pred^*(\Safe)}$ iff for every $b \in B_{\Bad}$, there is a $s \in B_{\pred^*(\Safe)}$ such that $s \leq b$.
Since $\Bad = U \setminus \Safe$, $\Bad \subseteq \uparrow B_{\pred^*(\Safe)}$ iff for every $b \in B_{\Bad}$, there is either $s \in B_{\pred^*(\Safe)}$ such that $s \leq b$, either $t \in B_{\Safe}$ such that $t\leq b$,
% si on est dans up Bad, il faut que ou bien on soit dans pred(Safe) ou bien on soit dans Safe
hence the resilience problem is decidable.
\end{proof}

@@

\begin{corollary}\label{B-up-up}
The bounded resilience problem is decidable for WSTS with effective pred-basis,
strong compatibility
 $\Safe=\uparrow \Safe$
and $\Bad=U \setminus \Safe$.
\end{corollary}

\begin{theorem}\label{k-up-up}
The % three %uniform 
$k$-resilience problem is decidable for WSTS with effective pred-basis, strong %upward-
compatibility, $\Safe=\uparrow \Safe$
and $\Bad=U \setminus \Safe$.
%	and \Bad is upward closed or downward closed.
\end{theorem}

\begin{proof}
Since $\Safe=\uparrow \Safe$ is upward closed, there exists a finite basis $B_{ \Safe}$ such that $\uparrow \Safe = \uparrow B_{\Safe}$. 
Moreover since $\mathscr{S}=(S,\rightarrow,\leq)$ is a WTSTS with strong upward compatibility,  $\pred^n(\Safe)=\uparrow \pred^n(\Safe)$ for all $n\in \N$ and $\pred^{\leq k}(\Safe)$ admits a finite basis $B_{\pred^{\leq k}(\Safe)}$. % Since $\mathscr{S}=(S,\rightarrow,\leq)$ is a WSTS  with effective pred-basis, we may compute a finite basis of $\pred^{\leq k}(\Safe)$ with the backward coverability algorithm. 
Since $U$  is upward closed, there exists a finite basis $B_{U}$ such that $U = \uparrow B_{U}$. % Moreover $ \uparrow B_{\Bad} \subseteq \uparrow B_{\pred^{\leq k}(\Safe)}$ iff for every $b \in B_{\Bad}$, there is a $s \in B_{\pred^*(\Safe)}$ such that $s \leq b$.
Since $\Bad = U \setminus \Safe$, $\Bad \subseteq \uparrow B_{\pred^{\leq k}(\Safe)}$ iff for every $b \in B_{\Bad}$, there is either $s \in B_{\pred^{\leq k}(\Safe)}$ such that $s \leq b$, either $t \in B_{\Safe}$ such that $t\leq b$,
% si on est dans up Bad, il faut que ou bien on soit dans pred(Safe) ou bien on soit dans Safe
hence the resilience problem is decidable.
\end{proof}
